---
title: "Author your first evidence-linked lesson"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Author your first evidence-linked lesson}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(rlearnxr)
```

R-LearnXR starts with an ordinary R result. The compiler preserves analytical evidence while lesson tasks ask learners to predict, inspect, explain, repair, transfer, and reproduce.

```{r}
fit <- prcomp(iris[, 1:4], scale. = TRUE)
evidence <- as_rlearnxr_evidence(fit)

stages <- c("orient", "predict", "run_r", "explore", "explain", "repair", "transfer", "reproduce")
tasks <- lapply(stages, function(stage) {
  task_spec(
    id = paste0("iris-", stage), type = stage,
    prompt = paste("Complete the", stage, "stage"),
    criteria = c(evidence = "Use an evidence ID when the task requires analytical support")
  )
})

lesson <- lesson_spec(
  id = "iris-pca", title = "Iris PCA evidence",
  outcomes = c("Interpret one PCA score", "Explain a linked observation", "Transfer the interpretation"),
  evidence = evidence, tasks = tasks
)
lesson
```

Use `compile_lesson(lesson, "iris-pca")` to write the portable project. The compiler is not executed in this vignette because package documentation builds must not modify the source tree.
