---
title: "Author your first evidence-linked lesson"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Author your first evidence-linked lesson}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(rclaimlab)
```

R-ClaimLab can start with an ordinary R result or a question-first local data workflow. The compiler preserves analytical evidence while lesson tasks ask learners to orient, predict, run R, inspect, explain, repair, transfer, and reproduce.

```{r}
lesson <- lesson_from_data(
  iris,
  analysis = "auto",
  dimensions = names(iris)[1:4],
  question = "Which measurements vary together, and which flowers have contrasting PCA scores?",
  intent = "reduce",
  unit_of_analysis = "one iris flower",
  decision_context = "learning to interpret multivariate variation",
  title = "Iris PCA evidence"
)
lesson
```

The generated contract includes method-specific PCA prompts, criteria, scaling and variance checks, misconceptions, visible R source, and reproducibility metadata. Use `compile_lesson(lesson, "iris-pca")` to write the portable project. The compiler is not executed in this vignette because package documentation builds must not modify the source tree.

Authors who already have a fitted object can still call `as_rclaimlab_evidence()`, define tasks with `task_spec()`, and assemble a custom `lesson_spec()`.
